### 2015-05-22 reports/paper/experiment.tex
update

\section{Experiment}
\subsection{Setup}
\subsubsection{Point localization}

@@

To test localization accuracy, an one meter by one meter grid was set up and the arrays are placed at the top left and top right corners of the grid. Fig~\ref{fig:setup_point} shows a picture of the setup. A total of $32$ testing locations are chosen uniformly in this.

\subsubsection{Movement tracking}
To test how well the arrays track movement, we mounted a rotating disk $40$ centimeter in diameter onto the grid at $(x=0$ cm$, y=-30$ cm$)$. Fig~\ref{fig:setup_circle} shows a picture of the sestup. A sound source is placed on the edge of the rotating disk and the arrays localizes the sound source as it rotates in a circle. In this experiment, we tested how accuracy changes with:
\begin{itemize}
\item different window sizes
\item different audio sources
\item different movement tracking filters
\item different movement speeds
\end{itemize}

To test how different sound sources impact localization quality, we conducted the experiments with three different sound sources:

\begin{description}[\IEEEsetlabelwidth{long a label}\IEEEusemathlabelsep]

@@

\item[Music A] A randomly picked music that has normal audio amplitude throughout experiment period. ``Honest Eyes'' by Black Tide was the music used.

\item[Music B] A randomly picked music with intermittent low amplitude sections. ``Canon'' was the music used.

@@

For each experiment conducted, two different movement filters were tests:
\begin{description}[\IEEEsetlabelwidth{Very long label}\IEEEusemathlabelsep]
\item[Averaging filter] localization for past $0.5$ seconds are averaged and outputed as current estimate.
\item[Kalman filter] A 2nd order Kalman filtering is used.
\end{description}

\subsection{Results}
\subsubsection{Point localization}
To test how accuracy varies with window size, the algorithm is fed with microphone data of different window size. Fig~\ref{fig:accuracy_vs_window} shows how accuracy changes with the window size for GCC, GCC\_PHAT and GCC\_PHAT\_SQRT. The error decreases as window size increases and plateaus after the window size exceeds around $10$ millisecond. The lowest error achieved is $2.53$ centimeters. It is achieved when window size is set to 12 millisecond and GCC\_PHAT is used for TDOA estimation.

Although accuracy improves with the window size, calculation time also increases with it. The part of calculation that depends on the window size is using cross correlation for TDOA estimation. Cross correlation can be calculated with Fast Fourier Transform (FFT) and the runtime is of order $O(N\log N)$. We measured how the computation time varies with window size and Figure~\ref{fig:speed_vs_window} shows the result. The runtime increases approximately linearly in the window size region of interest.

We also calculated the localization error for each tested point in the region. Figure~\ref{fig:error_distribution} shows the error distribution inside the grid. The error is below $3$ cm for most areas inside the region. There is one error spike in the mid-left region and we contribute this to audio source misplacecment becuase the error is fairly low and consistent around that spike.

@@

Fig~\ref{fig:wn} gives an intuitive representation of how accuracy changes with window size. When window size is small($1.02$ millisecond), the audio does not contain enough information to reliably estimate TDOA. The localization is noisy. As window size increases, the localization converges to the shape of ground truth circle. Fig~\ref{fig:err_win_circle} shows how the error changes with window size. The general trend is similar to that in point localization case. Error decreases as the window size increases and plateaus after it exceeds around $10$ milliseconds.

@@

Fig~\ref{fig:circle_wnn} to \ref{fig:circle_musicbn} shows results for experiments at normal speed, and Fig~\ref{fig:circle_wnf} to~\ref{fig:circle_musicbf} shows results at fast speed. By comparing localization error for each audio source between normal movement speed and fast movement speed, we find the localization error does not depend on how fast the sound sorce is moving. For example fig~\ref{fig:circle_musican} and fig~\ref{fig:circle_musicaf} shows that localization error is $1.289$ cm at normal movement speed and $1.291$ cm at fast movement speed.

>>>>

\section{Experiment}
We conducted two sets of experiments to evaluate the system's localization accuracy: one on point localization and the other on movement tracking.

\subsection{Setup}
\subsubsection{Point localization}

@@

An one meter by one meter grid was set up where the arrays were placed at the top left and top right corners of the grid. Fig~\ref{fig:setup_point} shows a picture of the setup. A total of $32$ testing locations were chosen uniformly in this grid. We reported the error as the average distance between our placement of the audio source and the location estimated from the arrays.

\subsubsection{Movement tracking}
To test how well the system tracks movement, we mounted a rotating disk $40$ centimeters in diameter onto the grid at $(x=0$ cm$, y=-30$ cm$)$. Fig~\ref{fig:setup_circle} shows a picture of the setup. A sound source is placed on the edge of the rotating disk and the arrays track the sound source as it rotates in a circle. In this experiment, we evaluated how accuracy changes with:
\begin{itemize}
\item window sizes
\item audio sources
\item movement tracking filters
\item movement speeds
\end{itemize}

To test how different sound sources impact localization quality, we conducted the experiments with three different sound sources:
\begin{description}[\IEEEsetlabelwidth{long a label}\IEEEusemathlabelsep]

@@

\item[Music A] A randomly picked music that has normal audio amplitude throughout the experiment period. \emph{Honest Eyes} by \emph{Black Tide} was the music used.

\item[Music B] A randomly picked music with intermittent low amplitude sections. \emph{Canon} was the music used.

@@

For each experiment conducted, two different movement filters were evaluated:
\begin{description}[\IEEEsetlabelwidth{Very long label}\IEEEusemathlabelsep]
\item[Averaging filter] localization for past $0.5$ seconds were averaged and outputed as current estimate.
\item[Kalman filter] A 2nd order Kalman filtering was used.
\end{description}

In the movement tracking experiments described above, we have the ground truth location of the circle, but not the exact location of the audio source at each moment during the movement. Therefore, the error is reported as the distance between the localized point to its closest point on the ground truth circle.

\subsection{Results}
\subsubsection{Point localization}
To test how accuracy varies with window size, the algorithm is fed with microphone data of different lengths, and the result is shown in fig~\ref{fig:accuracy_vs_window}. The error decreases as window size increases and plateaus after the window size exceeds around $10$ millisecond. The lowest error achieved is $2.53$ centimeters, which occurred when the window size is set to 12 millisecond and GCC\_PHAT is used for TDOA estimation.

Although accuracy improves with the window size, computation time also increases with it. The part of calculation that depends on the window size is using cross correlation for TDOA estimation. Cross correlation can be calculated with Fast Fourier Transform (FFT) and the runtime is of order $O(N\log N)$. We measured how the computation time varied with window size and Figure~\ref{fig:speed_vs_window} shows the result. The runtime increases approximately linearly in the window size region of interest.

We also calculated the localization error for each tested point in the grid. Figure~\ref{fig:error_distribution} shows the error distribution inside the grid. The error is below $3$ cm for most areas inside the grid. There is one error spike in the mid-left region and we contribute this to audio source misplacecment becuase the error is fairly low and consistent around that spike.

@@

Fig~\ref{fig:wn} gives an intuitive representation of how accuracy changes with window size. When window size is small($1.02$ millisecond), the audio does not contain enough information to reliably estimate TDOA. Which makes localization noisy. As window size increases, localization converges to the shape of the ground truth circle. Fig~\ref{fig:err_win_circle} shows how the error changes with window size. The general trend is similar to that in point localization case. Error decreases as the window size increases and plateaus after it exceeds around $10$ milliseconds.

@@

Fig~\ref{fig:circle_wnn} to \ref{fig:circle_musicbn} shows results for experiments at normal speed, and Fig~\ref{fig:circle_wnf} to~\ref{fig:circle_musicbf} shows results at fast speed. By comparing localization error for each audio source between normal movement speed and fast movement speed, we find that localization error does not depend on how fast the sound sorce is moving. For example fig~\ref{fig:circle_musican} and fig~\ref{fig:circle_musicaf} shows that localization error is $1.289$ cm at normal movement speed and $1.291$ cm at fast movement speed.
